

\documentclass[]{friggeri-cv}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
  allbordercolors=blue,
  pdfborderstyle={/S/U/W 1},
}

%\usepackage[document]{ragged2e}

\begin{document}

\header{André}{Melo}{Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside}
\section{contact}
Belo Horizonte, Brazil
+55-31-99228-2842
+55-31-2510-9939
~
\href{mailto:andrepontes@gmail.com}{andrepontes@gmail.com}
\href{https://github.com/andrepontesmelo}{github://andrepontesmelo}
\href{https://br.linkedin.com/in/andrepontesmelo}{linkedin://andrepontesmelo}
\section{languages}
portuguese
english
\section{programming}
C\#
Java
{\color{red} $\varheartsuit$} Ruby
C++
Javascript
\section{frameworks}
{\color{red} $\varheartsuit$} AngularJS
Selenium
ASP.NET
\section{libraries}
Capybara
NHibernate
Crystal Reports
\section{technologies}
 {\color{red} $\varheartsuit$} Linux
ElasticSearch
Amazon AWS
Virtualization
UI Automation
Cucumber
\section{databases}
MySQL
PostgreSQL
\section{IDEs}
{\color{red} $\varheartsuit$} Atom/Sublime
IDEA
Mono Develop
Visual Studio
\end{aside}
\section{intro}

I like to imagine what the future will look like and I build it in the mean time.

\section{experience}
\begin{entrylist}



\entry
{2016--NOW}
{JORNALEIRO}
{Belo Horizonte, Brazil}
{ Development of open source search engine of brazilian public journals using ElasticSearch / Ruby / Selenium / AngularJS / Android.
}

%------------------------------------------------

\entry
{2013--NOW}
{INDÚSTRIA MINEIRA DE JOIAS}
{Belo Horizonte, Brazil}
{ Software development for jewelry company.

  \begin{itemize}
    \item Development of full stack app using AngularJS + Java REST Api.
    \item Development C\# .NET app using  Crystal Reports / MySQL.
    \item Improved the worse business case that used to take 2 weeks and now takes 2 days by optimizing the company overall work-flow.
    \item Implemented bar code mapping using jewelry weight statistics.
  \end{itemize}
  }

%------------------------------------------------

\entry
{2012--2013}
{GAP @ AVENUECODE}
{San Francisco, USA}
{ Software development for fortune 500 client using agile methodology.
  \begin{itemize}
    \item Research and development that integrated functional tests to continuous integration pipeline using capybara-webkit headless driver.
  \end{itemize}
}

%------------------------------------------------

\entry
{2011--2012}
{BLOOMINGDALE'S @ AVENUECODE}
{New York, USA}
{ Software development for fortune 500 client using agile methodology.

  \begin{itemize}
    \item Implemented UI for checkout project using YUI and JSP.
  \end{itemize}
}
%------------------------------------------------

\entry
{2010--2011}
{COTAK SISTEMAS}
{Belo Horizonte, Brazil}
{ Build an autonomic library for configure and log distributed applications, and a map reduce library for scheduling a set of pair<algorithm, data> dynamically.

% Worked in development of a distributed computing cloud that automate UI web % interfaces, designed to feed automatic insurance quotes. Acquired experience in  distributed web systems, software architecture and technology research. Used C\# .NET and Amazon EC2 services. Had an opportunity to build an autonomic library for configure and log distributed applications, and a map reduce library for scheduling a set of pair<algorithm, data> dynamically.
%

  \begin{itemize}
    \item Freed the customer machine of running intense automation by moving the execution to controlled instances in the cloud.
    \item Improved the quality score index by implementing monitoring gadget.
    \item Development processing cloud that simulates random nodes death and avoid starvation attack.
  \end{itemize}
}

%------------------------------------------------

\entry
{2009}
{CONTRATANET}
{Belo Horizonte, Brazil}
{ ASP.NET Development in existing jobs and resumes site.
\begin{itemize}
  \item Development of new set of classes to generate matching and ranking between jobs and candidates.
  \item Using map-reduce to validate changes in regression tests.
  \end{itemize}
}

% %------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
%\entry
%{2015-NOW}
%{Android {\normalfont Developer Nanodegree}}
%{Udacity}

\entry
{2013}
{Communication \& Interpersonal {\normalfont Skills Training}}
{Dale Carnegie Training}


\entry
{2006}
{Article publication {\normalfont Color image enhancement through 2D histogram equalization, available at \url{http://goo.gl/iwGso6}}}
{Budapest, Hungary}
%------------------------------------------------


\entry
{2004--2010}
{{\normalfont Bachelor of} Computer Science}
{Federal University of Minas Gerais, Brazil}
%------------------------------------------------

\end{entrylist}




% \section{work and travel}
%
% \begin{entrylist}
%
% \entry
% {2006--2007}
% {parking lot {\normalfont operator}}
% {Mohegan Sun Casino, Connecticut, USA}
%
% \entry
% {2010}
% {supermarket {\normalfont operator}}
% {Publix Supermarkets, Florida, USA}
%
% \end{entrylist}
%
%
% \section{awards}
%
%
% \begin{entrylist}
%
% \entry
% {2003}
% {champion {\normalfont in robotics championship}}
% {Copa SUCESU, Minas Gerais, Brazil}
%
% \end{entrylist}
%
% \section{publications}
%
% MELO, A.; MENOTTI D.; SGARBI, E.; FACON, J.; ARAUJO, A. A. Realce de imagens coloridas através de equalização de histogramas 2D. In: Workshop of Undergraduate Students - SIBGRAPI 2005, 2005, Natal, Brasil. XVIII Brazilian Symposium on Computer Graphics and Image Processing, 2005. p. 1-8.
%
% MENOTTI D.; MELO, A.; ARAUJO, A. A.; FACON, J.; SGARBI, E. Color image enhancement through 2D histogram equalization. In: International Conference on Systems, Signals and Image Processing (IWS-SIP 2006), 2006, Budapest, Hungary. Proceedings of 13th International Conference on Systems, Signals and Image Processing (IWSSIP 2006), 2006. p. 235-238.
%
% \section{interests}
%
% \textbf{professionals:} distributed computing, big data, artificial intelligence, machine learning, information retrieval, Android and Linux \textbf{personals:} cooking, hiking,  chess, \textit{forró} (dance) and piano.
%
\end{document}
